---
title: "hw3"
format: html
---

https://github.com/nathanseaway/Homework_3.git

```{r}
library(tidyverse)
library(here)
library(gt)
library(flextable)
library(janitor)
library(readxl)

```

a.
To summarize my data I can take the mean of the number of times I apply sunscreen (response variable) compared between the two categorical groups: went to beach and did not go to beach (predictor variable). This allows me to compare the relation between going to the beach in a day and applying sunscreen, as I believe I apply sunscreen more on days when I go to the beach. 

b.
```{r}
library(dplyr)

sunscreen <- read.csv("sunscreen_fixed.csv") #reads csv file

sunscreen <- select(sunscreen, -Date, -Steps._Day, -Days._Spring, -Max._UV, -Max._Temp) #removes all variables besides suncreen application amount and beach attendance from file.

sunscreen <- sunscreen %>%

mutate(Beach = recode(Beach, "Y" = "Yes", "N" = "No")) #changes names of variable from y and n to yes and no.

library(ggplot2)

# Create summary with lowercase names

sunscreen_summary <- sunscreen %>%

group_by(Beach) %>% #groups data by beach attendance. 

summarise(

mean = mean(Frequency_Sunscreen_Application),

sd = sd(Frequency_Sunscreen_Application) #finds the means and standard deviation of sunscreen application by this grouping. 

)

# Plot

ggplot(sunscreen, aes(x = Beach, y = Frequency_Sunscreen_Application, color = Beach)) +
  geom_jitter(width = 0.1, height = 0, size = 2, alpha = 0.7) +
  scale_color_manual(values = c("No"= "lightgreen", "Yes"= "tan"))+
#plots beach attendace on x and number applications on y; sets size and appearance/color of data points.

  geom_point(data = sunscreen_summary, aes(x = Beach, y = mean),
             color = "lightgoldenrod", size = 4, inherit.aes = FALSE)+ #makes the mean points appear on graph 
  geom_errorbar(data = sunscreen_summary,
                aes(x = Beach, ymin = mean - sd, ymax = mean + sd),
                width = 0.2, color = "#687", inherit.aes = FALSE)+#adds error bars of means to graph. 
  labs(
    title = "Frequency Sunscreen Application by Beach Attendance",
    x = "Went to Beach: Yes or No",
    y = "Frequency of Sunscreen Application"
  ) #makes the labels of the graph.+
  theme_minimal()#sets the theme of the graph

```
c.
Figure 1. Distribution and means of frequency of sunscreen application by attendance to the beach (yes or no). Green points represent sunscreen application frequency for days where beach was not attended; brown to days where it was. Graph displays means and standard deviations of sunscreen application for both groups. Data from "sunscreen_fixed.csv" by Nathan Seaway from personal experience.

d.
```{r}
library(gt)
sunscreen_summary_rounded <- sunscreen_summary %>%
  mutate(
    mean = round(mean, 1),
    sd = round(sd, 1)
  )#rounds values in already created sunscreen summary table and makes it a new file. 

sunscreen_summary_rounded %>%
  gt() %>% #says we are using a gt table.
  tab_header(
    title = "Table of Sunscreen Application by Beach Attendance"
  ) %>% #give the table the following title
  cols_label(
    Beach = "Went to Beach",
    mean = "Mean Sunscreen Application",
    sd = "Standard Deviation"
  ) #gives the predictor variable, the mean, and the standard deviation titles new names. 
```

2.
a.
For my personal data, an affective visualization could represent the data that is displayed in my graph, but in a way that uses stylistic choices to demonstrate meaning behind the data. I think this would demonstrate differences in the mean, the standard deviation, and the general distributions of these two groups. I would want it to capture the larger skew of the no group as well as the slightly lower mean. I think I want my affective visualization to be a sort of sculptural representation of my data that plays around with literal objects to represent data. I'm thinking of using empty susncreen bottles, cut to different sizes and then paint to represent the data. 